### 2023-04-03 reachable-resilience.tex
removed the proof until I have a cleaner one
up

\begin{proof}
By Proposition~\ref{post*}, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
Let us now show that the downward-reachability problem is decidable for Petri nets.
Let us consider a downward closed set $D$ in a Petri net.
Let us consider $B$ a basis of the upward closed set $S \setminus D$.

@@

So downward-set reachability is decidable for PN.
\end{proof}

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong compatibility ~ & $\uparrow post^*$ effective & both  \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Corollary~\ref{bsrp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Corollary~\ref{bsrp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}

>>>>

\iffalse
\begin{proof}
By Proposition~\ref{post*}, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
Let us now show that the downward-reachability problem is decidable for Petri nets.
Let us consider a downward closed set $D$ in a Petri net.
Let us consider $B$ a basis of the upward closed set $S \setminus D$.

@@

So downward-set reachability is decidable for PN.
\end{proof}
\fi

@@

\begin{center}
\begin{tabular}{ | l | c | c | c | c |}
\hline  Hypothesis & strong upward compatibility ~ & $\uparrow post^*$ effective & both  \\ \hline
   SRP & Undecidable (Thm~\ref{srp up down}) & Decidable (Thm~\ref{post srp})  & Decidable (Thm~\ref{postcomputable})\\ \hline
   BSRP & Undecidable (Corollary~\ref{bsrp up down}) &  ??  & Decidable (Thm~\ref{ref ozkan}) \\ \hline
      kSRP & Undecidable (Corollary~\ref{bsrp up down}) & ?? & Decidable (Thm~\ref{ref ozkan}) \\ \hline
 \end{tabular}
\end{center}
